---
title: "Weight of Fish"
author: "Tiffany Alvarado"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
Perchwtall=lm(Weight~.-Weight,data=Perch)
summary.lm(Perchwtall)
library(leaps)
best_subsets <- regsubsets(Weight ~ . - Weight, data = Perch, nbest = 1)
summary_best_subsets <- summary(best_subsets)
summary_best_subsets$outmat
print(summary_best_subsets$outmat)
```
The adjusted rsquared is 0.9372
### Best Models
The best models are all the variables 
### Best Two regressor model
The model using height and widt are the best two regressors.

## Pike

```{r}
Perchwtall=lm(Weight~.-Weight,data=Pike)
summary.lm(Perchwtall)
library(leaps)
best_subsets <- regsubsets(Weight ~ . - Weight, data = Pike, nbest = 1)
summary_best_subsets <- summary(best_subsets)
summary_best_subsets$outmat
print(summary_best_subsets$outmat)
```

The adjusted rsquared is 0.9794
### Best Models
The best models are all the variables
### Best Two regressor model
The best two regressors models are Length1 and Length3
## Roach

```{r}
Perchwtall=lm(Weight~.-Weight,data=Roach)
summary.lm(Perchwtall)
library(leaps)
best_subsets <- regsubsets(Weight ~ . - Weight, data = Roach, nbest = 1)
summary_best_subsets <- summary(best_subsets)
summary_best_subsets$outmat
print(summary_best_subsets$outmat)
```
The adjusted rsquared is 0.821.
### Best Models
The best two models are all the variables.
### Best Two regressor model
The best two models are Length1 and Length3
## Final Summary Statements
in conclusion the helper file used is bestsubset regression the best regression model for perch was height and width the best regression model for pike was length1 and length3 the best regression model for roads were length3 and width